---
title: "The Health Vote"
author: "Tristan Kaiser"
date: "December 7, 2016"
output:
  pdf_document: default
  html_document: default
---

## R The Health Vote

This document will walk through an analysis of how people voted in the 2016 Presidential election by county, and various health-related measures.

#### Loading and cleaning the data

```{r, echo=T, message=F, warning=FALSE}
library(tidyverse)
library(magrittr)
```

The election and health data is all at the county level. Here the data is joined by State and County FIPS code.
```{r, message=F, warning=F, eval=T}
setwd("data")
voteData <- read_csv("clean/Pres_Election_Data_2016i.csv") %>%
  rename(County_FIPS_Code = COUNTY, State_FIPS_Code = STATEFIPS)

riskFactors <- read_csv("RISKFACTORSANDACCESSTOCARE.csv") %>%
  mutate(County_FIPS_Code = as.numeric(County_FIPS_Code),
         State_FIPS_Code = as.numeric(State_FIPS_Code))

fips_codes <- read_csv("fips_codes_website.csv") %>%
  mutate(County_FIPS_Code = `County FIPS Code`,
       State_FIPS_Code = `State FIPS Code`,
       combined_code =  paste(State_FIPS_Code, County_FIPS_Code, sep = ""))
       
fips_codes %<>% 
       mutate(County_FIPS_Code = as.numeric(County_FIPS_Code),
       State_FIPS_Code = as.numeric(State_FIPS_Code))

df <- left_join(riskFactors, voteData, by = c("County_FIPS_Code", "State_FIPS_Code"))
df <- left_join(df, fips_codes, by = c("County_FIPS_Code", "State_FIPS_Code"))


df[df == "-1111.1"] <- NA
df[df == "-1111"] <- NA
df[df == "-2222"] <- NA
df[df == "-2222.2"] <- NA
df[df == "-9999"] <- NA
df[df == "-1"] <- NA
df[df == "-2"] <- NA

```
### Exploring the data

Vote Map
```{r, message=F, warning=F, eval=T}
library(choroplethr)
library(choroplethrMaps)

df2 <- df
df2 %<>% dplyr::rename(region = combined_code)
df2 %<>% dplyr::rename(value = vote_difference)
df2 %<>% mutate(region = as.numeric(region))
df2 %<>% distinct(region, .keep_all = TRUE)
?county_choropleth
county_choropleth(df2,
                  title      = "2016 Presidential Vote Difference",
                  legend     = "Vote Difference",
                  num_colors = 7)
```

Do Hillary and Trump voters eat their vegetables?

```{r, message=F, warning=F, eval=T}

ggplot(df, aes(x = Few_Fruit_Veg, y = vote_difference)) +
  geom_point(aes(colour = victor)) +
  labs(x = "Few Fruits/Vegetables Consumed", y = "Vote differential (Trump = positive)") +
  theme_minimal()
```

